### 2020-08-17 treatise/1_introduction.tex
Revise: failure plot, two-stage version

\startsection [title={The Channel Sensing Problem}]

Multiple-input multiple-output (MIMO) communication system has been proposed to be incorporated into the 5G specification (Rappaport et.\ al.\ \cite [RSM13]).
With a large number of antennae of both transmitter and receiver sides, it is expected to provide a large signal gain.
However, its hardware overhead increases complexity and power consumption, and new precoders, and algorithms, are being invented to deal with this.
Especially, millimeter waves (hereafter mm-wave), with smaller wavelength, leads to higher frequency bands, and thus wider bands to be available.
In addition, the smaller closer spaced antennae makes it possible to increase the number of antennae.
This being said, with more antennae present, conventional training-based algorithms also increase in complexity and storage.

The design of new algorithms that addressed these issues is thus necessary, and ideally, we would like to know the expression of channel in advance.
The channel capacity is the major information theoretic metric to be considered in a communication system.
Roughly, the capacity of a MIMO channel at perfect channel state information is well-known to be in the form \m {\log \det \RB {I +\Ss {snr}}}, but the expression of channel is hardly always available, and in fact, the explicit dependence of capacity on relevant parameters is often a difficult problem (Goldsmith et.\ al.\ \cite [GJJ03]).
When the estimated channel is compromised, the ensuing analysis is also undermined.

It turns out that not only is the channel hard to estimate due to a large number of antennae, but the transmission is prone to noise corruption.
In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.

\stopsection
\startsection [title={The Dantzig Selector}]

It is a recent developement that the estimation of channels is facilitated by advances of the so-called \It {compressive sensing}.
A series of paper by Candès and Tao marks its advent.
They start by observing that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
%
\DispNum {N:p:Nm:Nm} {
\NC N_p \gg \NC N_m \NR
}
%
As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
Another example, to quote \cite [CaT07], is that of medical imaging: surely, since is not only expensive, but also harmful to the body, we may well obtain one image only, while the result can be critically important to assess the patient's well being.

But with insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
Of course, more assumption must be made to make the question meaningful, since any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.

They showed that in the noiseless case \cite [Can05], it is possible to recover the sparse signal, under a \m {\ell_1}-minimization program, revealing the phenomenon that fewer than \m {N_p} measurement suffices to resonstruct the \m {N_m}-dimensional signal, when it is sparse.
Later they established a stronger result \cite [CaT07] that, with another \m {\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too, but in doing so, we have to make a few carefully constructed, and seemingly random measurements.

From the computational perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
Indeed, relevent code has been put on the web for the reader to access and verify (Candès \& Romberg \cite [CaR05]).
In this paper we focus on DS, and we introduce several notions before we describe their work.

@@

And for given \m {s},
\Result
{Definition}
{
For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {Q}} satisfies \m {\d_s}-restricted isometry property (hereafter \m {\d_s}-RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if for all \m {s}-sparse \m {\V {x}}
%
\DispNum {1:2:Qx:22} {
\NC \RB {1-\d_s} \VNm {\V {x}} _2 ^2
\leq \NC \VNm {\M {Q} \V {x}} _2 ^2 \NR
%
\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2 ^2 \NR
}
}
%
It helps to think that \m {\M {Q}} is almost unitary up to relative error \m {\d_s}.

@@

Candès and Tao was able to show that, by Algorithm [3], \m {\V {x}} can be recovered, with the expected square error bounded with overwhelming probability.
Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program (hereafter LP), lending convex programming technique applicable.
The constant \m {\d_s} in Definition [2] is crucial, and here we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
One common design choice of \m {\M {Q}} proposed is that every entry of \m {\M {Q}} shall be i.i.d., and it can be established that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability (Baraniuk et.\ al.\ \cite [BDD08]).
Still, it remains unclear how to find RIP matrices efficiently, which became an active research area.

Meanwhile, back at the ranch, recall that the overhead of channel estimation has been a concern in the millimeter wave MIMO setting.
Luckily, physical evidences suggest that millimeter wave channels are in fact sparse in the frequency domain, and some scholars have thus applied compressive sensing techniques to the problem.
One of the first attempt has been Bajwa et.\ al.\ \cite [BHS10], where they argue that the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
What they explored was the estimation of single-antenna channel response with respect to time.
The accompanying paper by the same team (Bajwa et.\ al.\ \cite [BHR08]) shows that \m {X} is RIP for overwhelming probability, providing the ground for the former paper.

To illustrate, consider a linear time-invariant channel \m {y\SB {t} =\RB {x \star h} \SB {t} + z\SB {t}}, where \m {h\SB {t}} is the channel's impulse response, \m {y\SB {t}} is the output, and for each time index, signal \m {x\SB {t}} and noise \m {z\SB {t}} are both i.i.d.
Simply assuming \m {h} is sparse, we may express the convolution between \m {h} with \m {x} by a matrix \m {X}, so that \m {\V {y} =\M {X} \V {h} +\V {z}} for some \m {\M {X}}.
Then \cite [BHR08] showed that \m {\M {X}} is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice performance bounds drawing directly from \cite [CaT07].

\stopsection
\startsection [title={Orthogonal Matching Pursuit}]

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m {\M {Q} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
%
\item Initialize
%
\Disp {
\NC \V {r}
\LA \NC \V {y} \NR
%
\NC S
\LA \NC \varnothing \NR
}
\item Start the loop with counter \m {i \LA 1}.
\item Find
%
\DispNum {c:c:i0:ir} {
\NC c
\LA \NC \underset {i =0, \dots, N_p-1} {\Rm {argmax}}
\Nm {\M {Q} _{\SB {:,i}} \V {r}} \NR
}
%
and insert \m {S \LA S \cup {i}}.
\item Compute
%
\DispNum {Q:Q:QS:Qy} {
\NC \M {Q} ^\ddagger
\LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
%
\NC \V {r}
\LA \NC \V {y} -\M {Q} _{\SB {S}} ^\Adj \M {Q} ^\ddagger \V {y} \NR
}
\item Break if
%
\DispNum {r:2:h':h'} {
\NC \VNm {\V {r}} _2
<\NC \eta \NR
}
%
where \m {\VNm {\M {Q} ^\ddagger} _1} denotes the operator norm.
\item Output 
%
\DispNum {g:g:Qy:Qy} {
\NC \Hat {\V {g}}
\LA \NC \M {Q} ^\ddagger \V {y} \NR
}
\stopitemize
}
%
Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the estimated position where \m {\V {x}} is nonzero (where we have slightly abused the usage of subscript to indicate position indices).
From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a perfomance guarantee.

The matrix consisting of a collection of columns that likely spans \m {\V {x}} plays the role of the sensing matrix in the previous section.

\startsection [title={Further Development}]

OMP has since been applied in a variety of ways, and here we restrict our attention to channel estimation.
In fact, ever since, work on channel estimation seems to favored OMP instead of DS, nor other sparse algorithm, without clear justification, and this must have somthing to do with the simplicity of OMP implementation.

Alkhateeb et.\ al.\ \cite [AEL14] proposes an adaptive algorithm with a beam codebook for quantized angles of arrival and departure.
Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discusses the trade-off between number of OMP measurement and accuracy in OMP, applied on an all-phase-shifter beamformers, with quantized, non-uniform, predetermined angles.
Gao et.\ al.\ \cite [LGC16] present the jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals with restriction on positions of nonzero components.
Hu, Wang, and He \cite [HWH13] applies OMP to estimate quantized path delay of each OFDM subcarrier, assuming the channel gain in each path is stationary.
Lee, Gil, and Lee \cite [LGL16] considers a hybrid system similar to this paper, with the effective beamformer considered as sensing matrix, where they specially designed a set of quantized angles, and in their simulations permuted DFT matrix is used in analog stage.

@@

\startsection [title={Our Contribution}]

With all these efforts, current literature of compressive channel estimation, in our view, has not satisfyingly responded several aspects.
One notable drawback of OMP, as pointed out by \cite [GYG18], is that the quantized angle of the sensing matrix used dos not necessarily match the true ones.
At least in the uniform linear array setting, the angular domain can be used Fourier as sensing matrix, which researchers have correctly noted.
But the true angle of arrival and departure is often slightly off.
We can always use finer quantization, but that leads to higher complexity.
Moreover, researchers usually assume that the channel matrix has small norm, but further justifications and explicit bounds, depending channel parameters (say on sparsity and dimension), may be desired.

In this paper, we argue in favor of DS, rather than OMP, to be another viable solution that has been ignored.
To elaborate, we consider a system model where both digital and analog beamformer are i.i.d.\ random matrices, so that the effective beamformer serves readily as the sensing matrix with RIP.
Assuming uniform linear array, we apply a convex program inspired by DS so as to directly estimate the channel.
We shall see that a modified DS can be done on the angular domain instead of the spatial domain, and for complex numbers instead of real numbers.
Then along the lines of \cite [CaT07], we shall give a bound on expected square error, depending explicitly on the sparsity of the virtual channel matrix and the number of paths of the channel, which will surely future designers, in which the 
Furthermore, it holds under an overwhelming probability, which is also bounded quantitatively.

Lastly, we cast the convex probram to be a second order cone problem to facilitate efficient code.
We claim that, in view of numerical results, DS is often superior to OMP among other methods in terms of performance, but takes higher complexity.

>>>>

\startsection [title={Background: Estimation of MIMO Channel}]

Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification (Rappaport et.\ al.\ \cite [RSM13]).
With a large number of antennae on both transmitter and receiver, MIMO is expected to provide a large signal gain.
The appeal of MIMO includes multiplexing gain (with parallel transmission of data), diversity gain (with redundant transmission using space-time coding), and antenna gain (with beamforming).
The millimeter wave (mm-wave) is also suggested: its smaller wavelength results in higher frequency bands, and thus wider bands available.
The antennae may be closer-spaced, making it possible to increase their number.

However, MIMO also leads to hardware overhead and increases complexity and power consumption.
To design new algorithms that address these issues, it is necessary to obtain channel state information, so that channel capacity, among other metrics, can be calculated.
Not only is the channel estimation difficult due to a large number of antennae, but the transmission is prone to noise corruption.
With more antennae, conventional training-based algorithms also increase in complexity and storage.

\startsection [title={Compressive Sensing}]

Then, a recent developement called compressive sensing turns out to be relevant.
Generally speaking, it is a technique for reconstructing a signal in the case of underdetermined linear systems, if the sparsity of signal guarantees successful recovery in the majority of cases.
A more common situation is that some signals are not sparse in the original basis, but there exists a certain basis on which the signal is sparse, and fewer measurements suffice, though constructing such bases is another undertaking.

\blank [big]
\externalfigure [compressive-sensing.png] [wfactor=fit, hfactor=fit]

The figure shows the signal in both original basis and Hermite polynomials basis.
It is not sparse in the former, but is in the latter.
Thus, the recovery from just a few Hermite polynomial components are able to approximate it well.
(Source: Wikimedia Commons, retrived from \Uurrll {https://commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})

In the beginning, a Candès and Tao \cite [Can05] pointed out that in various statsitical applications the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
%
\DispNum {N:p:Nm:Nm} {
\NC N_p \gg \NC N_m \NR
}
%
They showed that in the noiseless case \cite [Can05], it is possible to recover the sparse signal, under a \m {\ell_1}-minimization program, revealing the phenomenon that fewer than \m {N_p} measurement suffices to resonstruct the \m {N_m}-dimensional signal, when it is sparse.

Indeed, usually any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.
But the sparsity constraint essentially restrict the underdetermined system so much that we obtain unique solution for most of the time.

As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
Another example is that of medical imaging: surely, since is not only expensive, but also harmful to the body, we may well obtain one image only, while the result can be critically important to assess the patient's well being \cite [CaT07].

\startsection [title={The Dantzig Selector}]

But with insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
A stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too, but in doing so, we have to make a few carefully constructed, and seemingly random measurements.

@@

\Result
{Definition}
{
For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {Q}} satisfies \m {\d_s}-restricted isometry property (hereafter \m {\d_s}-RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if for all \m {s}-sparse \m {\V {x}}
%
\DispNum {1:2:Qx:22} {
\NC \RB {1-\d_s} \VNm {\V {x}} _2 ^2
\leq \NC \VNm {\M {Q} \V {x}} _2 ^2 \NR
%
\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2 ^2 \NR
}
}
%
It helps to think that \m {\M {Q}} is almost unitary up to relative error \m {\d_s}.

@@

They were able to show \cite [CaT07] that Algorithm [3] recovers \m {\V {x}} with the expected square error bounded with overwhelming probability.

From the computational perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
Indeed, relevent code has been put on their website for the reader to access and verify (Candès \& Romberg \cite [CaR05]).

Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a Linear Program (hereafter LP), rendering convex programming technique applicable.
The constant \m {\d_s} in Definition [2] is crucial, and here we can't just take \m {\M {Q}} to be any unitary matrix, for which it is trivial that \m {\d_s =0}.
One common proposal is choosing every entry of \m {\M {Q}} to be i.i.d., and it can be established that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability (Baraniuk et.\ al.\ \cite [BDD08]).
However it remains a research problem to find RIP matrices efficiently.

Back at the ranch, recall that the overhead of channel estimation has been a concern in the mm-wave MIMO setting.
Luckily, physical evidences suggest that millimeter wave channels are in fact sparse in the frequency domain, and some scholars have thus applied compressive sensing techniques to the problem.
One of the first attempt has been Bajwa et.\ al.\ \cite [BHS10], where they argue that the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
What they explored was the estimation of single-antenna channel response with respect to time.
The accompanying note by the same authors (Bajwa et.\ al.\ \cite [BHR08]) shows that \m {X} is RIP for overwhelming probability, providing the ground for the IEEE paper.
Dealing with a linear time-invariant channel, \cite [BHR08] showed that if the convolution is seen as a linear system, the sensing matrix has RIP of overwhelmingly probability, and DS is ready to be applied, with some nice performance bounds drawing directly from \cite [CaT07].

\startsection [title={Orthogonal Matching Pursuit}]

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m {\M {Q} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
%
\item Initialize
%
\Disp {
\NC \V {r}
\LA \NC \V {y} \NR
%
\NC S
\LA \NC \varnothing \NR
}
\item Start the loop with counter \m {i \LA 1}.
\item Find
%
\DispNum {c:c:i0:ir} {
\NC c
\LA \NC \underset {i =0, \dots, N_p-1} {\Rm {argmax}}
\Nm {\M {Q} _{\SB {:,i}} \V {r}} \NR
}
%
and insert \m {S \LA S \cup {i}}.
\item Compute
%
\DispNum {Q:Q:QS:Qy} {
\NC \M {Q} ^\ddagger
\LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
%
\NC \V {r}
\LA \NC \V {y} -\M {Q} _{\SB {S}} ^\Adj \M {Q} ^\ddagger \V {y} \NR
}
\item Break if
%
\DispNum {r:2:h':h'} {
\NC \VNm {\V {r}} _2
<\NC \eta \NR
}
%
where \m {\VNm {\M {Q} ^\ddagger} _1} denotes the operator norm.
\item Output 
%
\DispNum {g:g:Qy:Qy} {
\NC \Hat {\V {g}}
\LA \NC \M {Q} ^\ddagger \V {y} \NR
}
\stopitemize
}
%
Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the number of estimated nonzero-position of \m {\V {x}}, which \cite [CaT07] calls support (here we have slightly abused the usage of subscript to indicate component indices).
From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a perfomance guarantee.
It is instructive to note that the matrix consisting of a collection of columns that likely spans \m {\V {x}} plays the role of the sensing matrix in the previous section.

Alkhateeb et.\ al.\ \cite [AEL14] proposes an adaptive algorithm with a beam codebook for quantized angles of arrival and departure.
Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discusses the trade-off between number of OMP measurement and accuracy in OMP, applied on an all-phase-shifter beamformers, with quantized, non-uniform, predetermined angles.
Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals with restriction on nonzero-positions.
Hu, Wang, and He \cite [HWH13] applies OMP to estimate quantized path delay of each OFDM subcarrier, assuming the channel gain in each path is stationary.
Lee, Gil, and Lee \cite [LGL16] consider a hybrid system similar to this paper, with the effective beamformer considered as sensing matrix, where they specially designed a set of quantized angles, and in their simulations permuted DFT matrix is used in analog stage.

@@

\startsection [title={Motivation and Contribution}]

Ever since, OMP has since been applied in a variety of ways.
Especially, work on channel estimation seems to favored OMP for its low complexity.
One notable drawback of OMP, as pointed out by \cite [GYG18], is that the quantized angle of the sensing matrix used dos not necessarily match the true ones.
Indeed, in the uniform linear array setting, DFT matrix can be used as sensing matrix, but the true angle of arrival and departure is often slightly off.
Meanwhile, as the nature of OMP is greedy, and it is dubious whether it achieves optimality.
In addition, the assumption that the channel matrix is sparse, at least, warrant justification.

In this treatise, we argue that DS is worth trying as an alternative.
As the next section shows, the effective beamformer serves readily as the sensing matrix with RIP.
Assuming uniform linear array, the sparsity may be exploited, and a convex program analogous to DS can be used for estimation, which ensures several desirable properties.
Along the lines of \cite [CaT07], we give a bound on expected square error, expressed in terms of on the sparsity and the number of paths, which will surely faciliate system design.
We show that it holds under an overwhelming probability, which is also bounded quantitatively.

Moreover, we illustrate that the convex program is equivalent to a linear program, for which several efficient algorithms are known.
In view of numerical results, DS is often superior to OMP among other methods, at the cost of higher complexity.

### 2020-08-17 treatise/2_problem_setting.tex
Revise: failure plot, two-stage version

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ \cite [ALS14]).
%
\DispNum {H:H:l0:ql} {
\NC \M {H}
=\NC \sum_{l=0} ^{L-1}
\a_l
\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \f_l'}
\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \th_l'}^\Adj \NR
}
%
The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\Rm {arr}}} is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \m {\V {a}} as
%
\DispNum {f:l:2p:2p} {
\NC \f_l
= \NC \RB {
  2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \f_l'
  \; \Rm {Mod}\; \RB {2\pi}
} \NR
%
\NC \th_l
= \NC \RB {
  2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \th_l'
  \; \Rm {Mod}\; \RB {2\pi}
} \NR
}
%
to get a simpler form
%
\DispNum {H:H:l0:ql} {
\NC \M {H}
=\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
\in \MB {C} ^{N_H \D N_H} \NR
}

@@

We consider the hybrid configuration at both transmitter and receiver end.
That is to say, each end consists of both digital and analog percoders and combiners, as follows.
In the transmitter end, there are, in order seeing from the end, digital precoder \m {\M {F} _B \in \MB {C} ^{N_R \D N_Y}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_R}}.
Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \m {\M {W} _R \in \MB {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_Y \D  N_R}}.

@@

And we will exploit the relation (whose proof is a strightforward application of definitions)
\Result
{Lemma}
{
Suppose \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}, \M {X} \in \MB {K} ^{N_2 \D N_3}, \M {B} \in \MB {K} ^{N_3 \D N_4}},
Then
%
\DispNum {v:B:BA:cX} {
\NC \Rm {vec} \SB {\M {A}\M {X}\M {B}}
= \NC \RB {\M {B}^\Tr \otimes \M {A}} \Rm {vec} \SB {\M {X}} \NR
}
}

@@

It, then, will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.

>>>>

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ \cite [ALS14]).
%
\DispNum {H:H:l0:ql} {
\NC \M {H}
=\NC \sum_{l=0} ^{L-1}
\a_l
\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \f_l'}
\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \th_l'}^\Adj \NR
}
%
The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\Rm {arr}}} is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \m {\V {a}} as
%
\DispNum {f:l:2p:2p} {
\NC \f_l
= \NC 2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \f_l'
  \; \Rm {Mod}\; \RB {2\pi} \NR
%
\NC \th_l
= \NC 2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \th_l'
  \; \Rm {Mod}\; \RB {2\pi} \NR
}
%
to get a simpler form
%
\DispNum {H:H:l0:ql} {
\NC \M {H}
=\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
\in \MB {C} ^{N_H \D N_H} \NR
}

@@

\externalfigure [system.png] [wfactor=fit, hfactor=fit]

We consider the hybrid configuration at both transmitter and receiver end, as shown in the figure.
That is to say, each end consists of both digital and analog percoders and combiners, as follows.
In the transmitter end, there are, in order seeing from the end, digital precoder \m {\M {F} _B \in \MB {C} ^{N_R \D N_Y}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_R}}.
Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \m {\M {W} _R \in \MB {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_Y \D  N_R}}.

@@

And we will exploit the relation (whose proof is a strightforward application of definitions)
\Result
{Proposition}
{
Suppose \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}, \M {X} \in \MB {K} ^{N_2 \D N_3}, \M {B} \in \MB {K} ^{N_3 \D N_4}},
Then
%
\DispNum {v:B:BA:cX} {
\NC \Rm {vec} \SB {\M {A}\M {X}\M {B}}
= \NC \RB {\M {B}^\Tr \otimes \M {A}} \Rm {vec} \SB {\M {X}} \NR
}
}

@@
